---
title: "&nbsp;"
output: html_document
classoption: landscape
params:
  team_rank: 4th
  team_color: "#f2b643"
  team_logo: https://upload.wikimedia.org/wikipedia/en/thumb/1/12/Boston_Bruins.svg/1200px-Boston_Bruins.svg.png
  team_city: Boston
  team_name: Bruins
  exp_win: 58.9
  proj_pts: 102.2
  playoffs: 87
  stanley_cup: 5.8
  lw_rank: 2nd
  c_rank: 13th
  rw_rank: 4th
  g_rank: 20th
  ld_rank: 8th
  rd_rank: 10th
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
library(tidyverse)
library(gt)

knitr::opts_chunk$set(
  echo = FALSE
)
```


<!-- <div style = 'text-align: center;background: '> -->

:::: {style="display: grid; grid-template-columns: repeat(4, lfr); grid-auto-rows: 300px;"}

::: {style="background:`r params$team_color`; grid-column-start: 1;grid-column-end:1;grid-row-start:1;grid-row-end:2"}

<!-- :::: {style="display: grid; background: `r params$team_color`; grid-area:1 / col1-start / last-line/ 6"} -->

## TEAM RANK: `r params$team_rank`

<br>
<br>

```{r, echo=FALSE, out.width="25%"}
knitr::include_graphics(params$team_logo)
```

<br>

# `r params$team_city`
# `r params$team_name`

```{r, echo=FALSE}
tibble(
  metric = c("EXPECTED WIN %: ", "PROJ POINTS: ", "PLAYOFFS: ", "STANLEY CUP: "),
  vals = c(params$exp_win, params$proj_pts, params$playoffs, params$stanley_cup)
) %>% 
  gt() %>% 
  opt_table_lines("none") %>% 
  cols_label(metric = "", vals = "") %>% 
  cols_align("left", columns = 1) %>% 
  cols_align("right", columns = 2) %>% 
  tab_style(
    style = cell_text(font = "Fira Mono", color = "white"),
    locations = cells_body()
  ) %>% 
  tab_style(
    style = cell_fill(alpha = 0),
    locations = cells_body()
  ) %>% 
  fmt_percent(columns = vals, scale_values = FALSE, rows = c(1,3,4), decimals = 1) %>% 
  fmt(columns = vals, rows = 2,
      fns = function(x){
        round(x, digits = 1) %>% paste0(., "&nbsp") %>% 
          gt::html()
      }) %>% 
  tab_options(table.background.color = "#ff000000")
```


```{r, echo = FALSE}
tibble(c1 = c("<br>STAR<br><br>", "<br>TOP<br><br>"),
       c2 = c("<br>LEGEND<br><br>", "<br>MIDDLE<br><br>"),
       c3 = c("<br>FRINGE<br><br>", "<br>BOTTOM<br><br>")) %>% 
  mutate(c1 = purrr::map(c1, gt::html),
         c2 = purrr::map(c2, gt::html),
         c3 = purrr::map(c3, gt::html)) %>% 
  gt() %>% 
  tab_style(style = cell_borders(color = "white", weight = px(4)),
            locations = cells_body()) %>% 
  tab_style(style = cell_borders(color = "white", weight = px(4)),
            locations = cells_column_labels()) %>% 
  tab_style(style = list(
    cell_fill(color = "#f8ba00"),
    cell_text(color = "white", weight = "bold", font = "Fira Mono")),
            locations = cells_body(1, 1)) %>% 
  tab_style(style = list(
    cell_fill(color = "white"),
    cell_text(color = "black", weight = "bold", font = "Fira Mono")),
            locations = cells_body(2, 1)) %>% 
  tab_style(style = list(
    cell_fill(color = "#fa998e"),
    cell_text(color = "white", weight = "bold", font = "Fira Mono")),
            locations = cells_body(3, 1)) %>% 
  tab_style(style = list(
    cell_fill(color = "black"),
    cell_text(color = "white", weight = "bold", font = "Fira Mono")),
            locations = cells_body(1, 2)) %>% 
  tab_style(style = list(
    cell_fill(color = "darkgrey"),
    cell_text(color = "white", weight = "bold", font = "Fira Mono")),
            locations = cells_body(2, 2)) %>% 
  tab_style(style = list(
    cell_fill(color = "lightgrey"),
    cell_text(color = "white", weight = "bold", font = "Fira Mono")),
            locations = cells_body(3, 2)) %>% 
  cols_align("center") %>% 
  cols_label(c1 = "", c2 = "", c3 = "") %>% 
  tab_options(
    table.border.top.color = "white",
    column_labels.border.top.color = "white"
  ) %>% 
  cols_width(1 ~ px(90),
             2 ~ px(90),
             3 ~ px(90)) 
```
:::

::::

<!-- :::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"} -->

::: {style='grid-column-start: 2;grid-column-end:2;grid-row-start:1;grid-row-end:1;'}
## LW `r params$lw_rank`

```{r}
# str(iris)
```
:::

::: {style='grid-column-start: 3;grid-column-end:3;grid-row-start:1;grid-row-end:1;'}

## LW `r params$c_rank`

And this block will be put on the right:

```{r}
# plot(iris[, -5])
```
:::

::: {style='grid-column-start: 4;grid-column-end:4;grid-row-start:1;grid-row-end:1;'}

## LW `r params$rw_rank`

And this block will be put on the right:

```{r}
# plot(iris[, -5])
```
:::

<!-- :::: -->

<!-- Bottom row -->

<!-- :::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"} -->

::: {style='grid-column-start: 2;grid-column-end:2;grid-row-start:2;grid-row-end:2;'}
## G `r params$g_rank`

```{r}
# str(iris)
```
:::

::: {style='grid-column-start: 3;grid-column-end:3;grid-row-start:2;grid-row-end:2;'}

## LD `r params$ld_rank`

And this block will be put on the right:

```{r}
# plot(iris[, -5])
```
:::

::: {style='grid-column-start: 4;grid-column-end:4;grid-row-start:2;grid-row-end:2;'}

## RD `r params$rd_rank`

And this block will be put on the right:

```{r}
# plot(iris[, -5])
```
:::

::::
